Standard Candle Cosmology With Incomplete Spectroscopic Classification

### 2015-11-03 doc/article.tex
adding more stuff to section 3

\section{Tasks}
Here are a list of initial tasks and ingredients needed to proceed.
\subsection{Photometric Selection}
Here are desired properties of the set (or sets) of objects obtained from photometric selection.
\begin{itemize}
\item Sufficient data-quality to have a chance at photometric classification.
SNe~Ia do look different from other transients: the principal source of type  ambiguity
comes from poor signal-to-noise and poor temporal/wavelength sampling.
\item A large set of likely SNe~Ia.
\item All objects with photometry-only must have spectroscopically-typed analogs, preferably though not necessarily at the same redshift.  SNe~Ia subpopulations whose characteristics
are unconstrained are not useful for cosmology.
\item Obvious non-Ia's from populations that could be misconstrued as SN~Ia.  For example,
a non-Ia at low redshift could be
mistaken to be SN~Ia at high redshift due to degraded signal.
\item Exclusion of objects that are not part of populations that could be misconstrued as SN~Ia.
They would pollute inference of the non-Ia population.
\end{itemize}

A clean deliverable would be:
\begin{itemize}
\item Determination of flux thresholds for each photometric point given
a $S/N$ threshold
\begin{equation}
threshold(point, S/N).
\end{equation}
If we work in the sky-noise dominated regime, I believe this information is already
calculated by DM.
\end{itemize}
\subsection{Others}

\begin{itemize}
\item Identification of selection criteria for spectroscopic success, as a function
of data.
\item A rates model for transient types and subtypes
\begin{equation}
\pi(z;r).
\end{equation}
\item Decision on how to model the distribution of $x_1$ and $c$.  For a first try a
single normal distribution seems sufficient but do we want to be more ambitious?
\item A non-Ia transient model.  Much of its usage is in classification, PSNID or
Karpenka could be places to start.
\item Calibration model and uncertainties. Assuming we work with zeropoints
$p(Z)$ is needed.
\item Data! Spectroscopic Type and uncertainties, Spectroscopic redshifts and
uncertainties, galaxy properties and uncertainties, host-galaxy associations
and uncertainties, photometry and uncertainties.
\item Determine the mechanics of doing the analysis.  A Bayesian MCMC could produce posteriors, which sampler that best suits our needs? Is a frequentist
analysis technically unfeasible? If redshifts were free to wander I would think so, but maybe
it is possible in this model.
\end{itemize}

>>>>

\section{Tasks}
Here are a list of initial tasks and ingredients needed to proceed.
\subsection{Photometric Selection}
Here are desired properties of the set (or sets) of objects obtained from photometric selection.
\begin{itemize}
\item Sufficient data-quality to have a chance at photometric classification.
SNe~Ia do look different from other transients: the principal source of type  ambiguity
comes from poor signal-to-noise and poor temporal/wavelength sampling.
Having enough points with sufficient signal-to-noise over three adjacent bands over a 
sufficiently large time window.
\item A large set of likely SNe~Ia.
\item All objects with photometry-only must have spectroscopically-typed analogs, preferably though not necessarily at the same redshift.  SNe~Ia subpopulations whose characteristics
are unconstrained are not useful for cosmology.
\item Obvious non-Ia's from populations that could be misconstrued as SN~Ia.  For example,
a non-Ia at low redshift could be
mistaken to be SN~Ia at high redshift due to degraded signal.  
\item Exclusion of objects that are not part of populations that could be misconstrued as SN~Ia.
They would pollute inference of the non-Ia population.
\end{itemize}

A clean deliverable would be:
\begin{itemize}
\item Determination of flux thresholds for each photometric point given
a $S/N$ threshold
\begin{equation}
threshold(point, S/N).
\end{equation}
If we work in the sky-noise dominated regime, I believe this information is already
calculated by DM.
\end{itemize}

\subsection{Spectroscopic Selection}
Identification of selection criteria for spectroscopic success, as a function
of data.

\subsection{Relative Rates}
\label{rates:sec}
A rates model for transient types and subtypes
\begin{equation}
\pi(z;r).
\end{equation}
\subsection{SALT2}
Decision on how to model the distribution of $x_1$ and $c$.  For a first try a
single normal distribution seems sufficient but do we want to be more ambitious?
\subsection{Non-Ia Transient Model}
Needed is a model(s) for non-transients that could be mistaken as SN~Ia:
both a description of the time-evolving SED and the relative rates
with respect to Type~Ia's (see \S\ref{rates:sec}).

The SED model is of the time evolving luminosity (or more precisely $\mathcal{M}$)
for the range of possible non-Ia's.  It describes not only colors and light curve shapes,
but also absolute magnitude.  Its parameters can be constrained part of the
global analysis, indeed the pdf of the absolute magnitude is candidate.

As much of its usage is in classification, PSNID is a place to start.
Natasha Karpenka has been compiling a descriptions of non-Ia-Type~I's.  Can these
be packaged into the following deliverable?

The deliverable is a parameterized SED model that can be accessed through
an interface such as $L(t,\lambda; \text{Non-Ia parameters})$.

\subsection{Host-Galaxy Parameter Determination}
Although a different group within DES is charged with deriving properties
of galaxies (including our hosts), results do not seem to be forthcoming.
Mat has said that there is a group within the SNWG interested in
taking over this task.  Chris has discussed getting deep
co-adds of galaxies uncontaminated by supernova light.
Can we confirm who is part of this effort, if there is forward momentum,
and get a single name that used as the point of contact?

The deliverable are galaxy properties and a covariance matrix of their uncertainties,
which are treated in the analysis as data.

\subsection{NIR Data}
VISTA NIR data have important probative value that can enhance about all aspects
of our analysis even if available for a subset of objects.
We should decide our intents on the timing of the use of this data.
For example, on whether we plan on a DES-only paper and DES+NIR, and if
we want to focus efforts on the former in the short term.

\subsection{Others}

\begin{itemize}
\item Calibration model and uncertainties. Assuming we work with zeropoints
$p(Z)$ is needed.
\item Data! Spectroscopic Type and uncertainties, Spectroscopic redshifts and
uncertainties, galaxy properties and uncertainties, host-galaxy associations
and uncertainties, photometry and uncertainties.
\item Determine the mechanics of doing the analysis.  A Bayesian MCMC could produce posteriors, which sampler that best suits our needs? Is a frequentist
analysis technically unfeasible? If redshifts were free to wander I would think so, but maybe
it is possible in this model.
\end{itemize}
